Theories of deliberated choice

### 2023-10-20 simple.tex
Rm redundant (less clear) thm

  To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
\end{remark}
\begin{conjecture}
  Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
  $C$ is falsifiable iff these new elements are necessarily in $C$.
\end{conjecture}
\begin{proof}
  This seems false. (Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
  % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$). Assume that $\cup S$ is total and right-unique and is not in $C$.
  % Let us show that $C$ is not falsifiable.
  % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
  % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
  % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
\end{proof}
\begin{theorem}[To check considering finiteness of observations]
  Given a claim $C$, consider the sets $S \subseteq C^\subseteq$ such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and such that $\cup S$, considered as a relation on $(I × \allhist) × P$, is right-unique (that is, $\cup S$ forms a new relation $\allleadstog$).
  $C$ is falsifiable iff all such sets $S$ satisfy $\cup S \in C$.
\end{theorem}
\begin{proof}
  Consider such $S$.
  Assume that $\cup S$ is not in $C$.
  Let us show that $C$ is not falsifiable.
  Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  Define $O \in (\incr(\allhist))^I \suchthat \theta^{-1}(P) \subseteq O$. Thus, $O \in \set{\theta^{-1}(P) \suchthat \theta \in S}$. Pick an element $\theta' \in S \suchthat (\theta')^{-1}(P) = O$. We have $\theta' \in C^\subseteq$ and $\theta^{-1}(P) \subseteq (\theta')^{-1}(P)$.
  Also, $\theta \subseteq \cup S$, and $\cup S$ is right-unique, so $\theta$ coincides with $\theta'$ on its domain (meaning that $\theta = \restr{\theta'}{\theta^{-1}(P)}$). It follows that $\theta \subseteq \theta'$. As $C^\subseteq$ is downwards-closed, this concludes.

  Now, assume that $C$ is not falsifiable and pick any ${\allleadstog} \notin C \suchthat \forall \theta \in \Theta, \theta \subseteq {\allleadstog}: \theta \in C^\subseteq$.
  Given any $O \in (\incr(\allhist))^I$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.
  Define $S = \set{\restr{\allleadstog}{O} \suchthat O \in (\incr(\allhist))^I}$.
  The set $S$ satisfies the required conditions and $\cup S = {\allleadstog}$, thus, $\cup S \notin C$.
\end{proof}
Here is another way (perhaps more illuminating) of stating the same thing.
\begin{remark}
  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhist))^I)}$.
  (Also, any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhist)^J}$.)
  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.

>>>>

  To obtain non fals, need to form a relation whose all decompositions into incr associations are in $C$, but itself not in $C$.
\end{remark}
\begin{conjecture}
  Given a claim $C$, consider the subsets of $(\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ whose union, considered as a relation on $(I × \allhist) × P$, is total and right-unique (that is, the subsets that form a new relation $\allleadstog$).
  $C$ is falsifiable iff these new elements are necessarily in $C$.
\end{conjecture}
\begin{proof}
  This seems false. (Consider $I = \set{i_1, i_2}$ and $\args = \set{a, b}$ and $\psi$ is ${\ileadsto[i_1]} = {\ileadsto[i_2]}$ and $S = \set{R_1, R_2, …}$ with $R_1$ are all sequences starting with $a$ sent to $p$ and $R_2$ are all sequences starting with $b$ sent to $p' ≠ p$.)
  % Consider $S \subseteq (\cup_{A \in \max \incr(\allhist)}P^A)^I \cap C^\subseteq$ (thus each $R \in S$ is a relation $R \subseteq (I × \allhist) × P$). Assume that $\cup S$ is total and right-unique and is not in $C$.
  % Let us show that $C$ is not falsifiable.
  % Define ${\allleadstog} = \cup S$, pick any $\theta \in \Theta, \theta \subseteq {\allleadstog}$ and let us show that $\theta \in C^\subseteq$.
  % Let us show that $\exists R \in S \suchthat \theta \subseteq R$.
  % Pick any triple $t \in \theta$. Thus, $t \in \cup S$. Thus, for some $R \in S$, $t \in R$. And $R \in C^\subseteq$.
  % Pick any two triples $t, t' \in \theta$. Wlog, $\hist \subseteq \hist'$.
\end{proof}

\begin{remark}
  Any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in (\finite(\incr(\allhist))^I)}$.
  (Also, any relation $\allleadstog$ is equivalent to $\cup \set{\restr{\allleadstog}{O} \suchthat O \in \cup_{J \subseteq_\finite I} (\allhist)^J}$.)
  Conversely, any set $S$ of observations such that $\set{\theta^{-1}(P) \suchthat \theta \in S} = \incr(\allhist)^I$ and $\cup S$ is right-unique corresponds to a unique relation $\cup S = {\allleadstog}$.
  Thus, there is a bijection between the set $\mathcal{S}$ of such sets $S$ and the set of leads to relations.
